%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Characterizing cortico-cerebellar connectivity in the developing cerebellum, and using machine learning to identify risk predictors of neurodevelopmental disorders}
    {ICoN Postdoctoral Fellow at MIT} % Job title
    {\href{https://maedbhk.github.io/MIT-Projects/}{\textbf{MIT Projects [link]}}}
    {2022-} % Organization
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Adopted a transdiagnostic approach to establish how brain differences relate to cognitive difficulties in childhood. Trained an artificial neural network on a sample of 4,000 participants to capture non-linear relationships in cognitive profiles and cortical morphology data.}
		\item {Identified risk predictors for self-harm and suicide attempt in an adolescent population. Used natural language processing (NLP) to decode unstructured electronic health records and predictive modeling to identify critical features from structured clinical profiles. Overall goal is to use models to inform clinical outcomes.}
		\end{cvitems}
    }


%---------------------------------------------------------
  \cventry
  	{Investigating cortico-cerebellar contributions to cognition. First-author publications in \textit{Nature Neuroscience}, \textit{ELife}, \textit{Neurobiology of Language}}
    {Ph.D. Researcher at UC Berkeley} % Job title
    {\href{https://github.com/maedbhk/}{\textbf{Berkeley Projects [Link]}}}
    {2017-2022} % Organization
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and tested a large-scale (5 session) fMRI and behavioral study to investigate how the cerebellum learns, and developed machine learning pipelines to predict cognitive function across learning. Tested patients with spinocerebellar ataxia on a series of cognitive tasks to assess cerebellar deficits. Analyzed post-mortem brain data to create a transcriptomic map of the cerebellum. Co-developed SUITPy, an open-source Python library to visualize brain data.}
        \item {Prioritized taking classes in advanced statistics and computer science to analyze high-dimensional neural data.} 
        \item {Led a team of 5 to design and collect 300 experimental hours of functional magnetic resonance imaging (fMRI) data (during COVID-19 pandemic).}
        \item {Recorded >15 hours of varsity athletes, and implemented markerless labeling of videos to understand human performance in predicting actionn \href{https://github.com/maedbhk/action_prediction}{\textit{[link]}}.}
        \item {Co-wrote an R35 grant that received 5-year funding from the NIH. Managed an institutional review board (IRB) protocol for fMRI experiments.}
        \item {Created a widely adopted mentorship agreement for research assistants to ensure transparency and accountability in mentoring practices \href{https://drive.google.com/file/d/1m7PI3lnOZpKdLxWAtxvjcXeQ3xG7I8r0/view?usp=sharing}{\textit{[link]}}.}
        \item {Co-led a journal club for undergraduate research assistants, instructing them on the scientific method, data analysis, and statistics.}
        \item {Mentored two undergraduate students in designing and writing up honors thesis projects. One student was awarded a \href{https://psychology.berkeley.edu/sites/default/files/undergraduate-program/swanaward_application_2019-2020.pdf}{\textit{Swan prize [link]}} for their work, and presented at a national conference.}
      \end{cvitems}
      }
    
%---------------------------------------------------------
  \cventry
    {Mapping the human cerebellum. Publications in \textit{Brain}, \textit{NeuroImage}, \textit{Frontiers}}
    {M.Sc. Graduate Student Researcher (2015-2017)} % Job title
    {\href{https://github.com/maedbhk/}{\textbf{Western Projects [Link]}}}
    {Western University} % Organization
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a novel and highly downloaded map {\href{http://www.diedrichsenlab.org/imaging/mdtb.htm}{\textit{[link]}}} of the human cerebellum using machine learning and advanced statistics.}
      	\item {Led a team of 2 to design and collect a 26-task, 6-session fMRI and behavioral experiment, totaling 250 hours of data collection {\href{http://www.diedrichsenlab.org/imaging/AtlasViewer/viewer.html}{\textit{[link]}}}.}
      	\item {Initiated a collaboration with scientists from Stanford University to use natural language processing to assign cognitive labels to the human cerebellum {\href{https://cognitiveatlas.org/}{\textit{[link]}}}. Developed programming pipeline for other researchers to replicate my novel approach, and wrote supporting documentation.}
      	\item {Invested in open-source science. My data, which are publicly available, have been downloaded >200 times {\href{https://openneuro.org/datasets/ds002105/versions/1.1.0}{\textit{[link]}}}.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
