%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Mentorship}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

 
%---------------------------------------------------------
  \cventry
    {Sep. 2019 - May 2021} % Date(s)
    {Honors Thesis Students} % Student
    {Shannon Lee; Sienna Bruinsma} 
    {Cognitive Science; Psychology} % Position
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Shannon Lee's thesis developed eye-tracking and context models to inform social learning.}
        \item {Sienna Bruinsma's thesis evaluated the functional role of the cerebellum in linguistic processing using neuropsychology.}
      \end{cvitems}
    }
    
    
%---------------------------------------------------------
  \cventry
    {Jan. 2021 - May 2021; Sep. 2019 - May 2020} % Date(s)
    {Undergraduate Research Assistants} % Student
   	{Zanib Naaem; Yiling Kao}
   	{Psychology; Computer Science}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Zanib Naaem tested healthy college-aged students on a multi-session eye-tracking and behavioral learning project.}
        \item {Yiling Kao developed a verb generation task and used machine learning to study speech envelopes.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Sep. - Dec. 2020; Jan. - May 2020; Sep. - Dec. 2018} % Date(s)
    {Ph.D. Rotation Students} % Student
    {Amanda LeBel; Jacob Ziontz; Mark Gorenstein}
    {Neuroscience}
   {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Amanda LeBel developed encoding models using speech features to study task-evoked cerebellar activity.}
        \item {Jacob Ziontz set up fMRI preprocessing scripts (BIDS and fMRIPrep) on multi-session cerebellar data.}
        \item {Mark Gorenstein worked on preprocessing pipelines for cerebro-cerebellar connectivity models.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Sep. - Dec. 2018} % Date(s)
    {Post-Baccalaureate Students} % Student
    {Dylan Benkley}
    {Psychology}
   {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Dylan Benkley conducted a literature review on the role of the cerebellum in social cognition.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
