%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Public Service \& Outreach}

%-------------------------------------------------------------------------------
\cvsubsection{Committees \& Policy}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry 
    {MIT} % Location
    {Council on Family and Work}
    {\href{https://drive.google.com/file/d/1KEYOxyQlJCVVjhXWzmFyOpVgB2zHHPXx/view?usp=sharing}{\textbf{Postdoc Representative [Link]}}}
    {Sep. 2022 -} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Nominated to be the postdoc representative on the MIT Council on Family and Work based on prior work as part of MIT POWER (women postdocs at MIT). Conducted a project on postdoc satisfaction with parental and childcare policies at MIT (\href{https://drive.google.com/file/d/1fMhWOel-4FEX4SDK02NLmEE5upsajKBK/view?usp=sharing}{\textit{survey [link]}} and \href{https://docs.google.com/presentation/d/1VMELasSNFhN1QjrGt7P7uAFt0IQIIH-c8I0jKGWZdzI/edit?usp=sharing}{\textit{results [link]}})}.
        \item {As a member of the council, it is our responsibility to: 1) identify family and work-related issues, 2) establish a process to evaluate and respond to these issues, and 3) make periodic recommendations to MIT's senior officers about courses of action relevant to these specific issues.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry 
    {MIT} % Location
    {Science Policy Group - Executive Visit to D.C.}
    {\textbf{Member}} % Organization
    {Sep. 2022 -} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Selected to attend an executive visit trip to Washington, DC to meet with agency leaders from NSF, USDS, EPA, NASA to discuss science policy.}
        \item {Led a meeting at the White House office of science and technology policy (OSTP) with Obama's former CTO, Megan Smith.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry 
    {University of California, Berkeley} % Location
    {Graduate Assembly Students of Psychology}
    {\textbf{Member and RSO Signatory}} % Organization
    {Sep. 2018 - Mar. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Recognized need for formal mentor-mentee agreements in the UC Berkeley psychology department \href{https://drive.google.com/file/d/1m7PI3lnOZpKdLxWAtxvjcXeQ3xG7I8r0/view?usp=sharing}{\textit{[link]}}. Assembled and co-led working committee to create policy to improve lab culture and mentor-mentee relationships.} 
        \item {Wrote initial draft for 10-page policy document on mentorship and lab policy agreements \href{http://ivrylab.berkeley.edu/uploads/4/1/1/5/41152143/cognac_lab_policies_19feb2021.pdf}{\textit{[link]}}. Advised leadership on implementation of new departmental policies. Since Sep. 2021, 35/42 faculty have created lab policy documents.}
        \item {Advisor on Berkeley Psychology state of the department annual meeting \href{https://drive.google.com/file/d/1wD7y5gW39EU4vQUyhcrO7Fra1Ttc_HyG/view?usp=sharing}{\textit{[link]}}, led team to conduct data analytics and statistics to translate graduate student concerns into policy recommendations. Used data and statistics to highlight funding discrepancy between neuroscience and clinical psychology students, resulting in a 20\% yearly increase in graduate student stipends.}
        \item {Provided data analytics to improve efficiency of phone banking for Psychology "Big Give". Contacted 10-fold more donors than previous year.}
        \item {Liaison officer between Berkeley development office and external donors. Organized faculty fundraisers in Silicon Valley.}
      \end{cvitems}
    }

    
  \cventry
    {European Union}
    {European Federation of Psychology Students' Association} % Committee
    {\href{https://jeps.efpsa.org/articles/10.5334/jeps.401/}{\textbf{Editor [Link]}}} % Position
    {Jan. 2016 - May 2016} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheaded initiative to pre-register scientific results in the Journal of European Psychology Students, a first for student journals worldwide.}
        \item {Advised organization leadership on best practices for successful implementation of pre-registration and authored journal article (>3500 views).}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
  	{Western University} % Location
  	{Schulich School of Medicine Graduate Council} % Committee
    {\textbf{Secretary}} % Position
    {Sep. 2015 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided budget evaluation of graduate student insurance plan to council. Served as student liaison officer.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
  	{Trinity College, Dublin}
  	{Niteline (Student Helpline)} % Committee
    {\textbf{Publicity Officer}} % Position
    {Sep. 2011 - May 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided practical program consultation to student helpline \href{https://niteline.ie/}{\textit{[link]}}.}
      \end{cvitems}
    }

\cvsubsection{Communication \& Administration}

%---------------------------------------------------------
  \cventry 
    {University of California, Berkeley} % Location
    {Graduate Assembly Students of Psychology}
    {\href{https://psychblog.berkeley.edu/opinion/2019/09/09/Graduate-School-Advice/}{\textbf{Writer/Contributor [Link]}}} % Organization
    {Sep. 2019 - May 2021} % Date(s)
    {
      \begin{cvitems} 
      	\item {Created, managed, and edited \href{https://psychblog.berkeley.edu/blog/}{\textit{[link]}} Berkeley Psychology blog to spotlight graduate student research.}
      	\item {Co-founded and co-operated Twitter account for Berkeley Psychology \href{https://twitter.com/BerkeleyPsych}{\textit{[link]}}. Increased follower count to >1500 after 2 years.}
      	\item {Co-Writer of Psychology newsletter \href{https://psychology.berkeley.edu/sites/default/files/newsletters/2021spr_fullnewsletter_v2.pdf}{\textit{[link]}} (>2000 circulation). Included profiles on graduates to strengthen ties with alumni community.}
      \end{cvitems}
    }
    
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {European Union}
    {\textbf{Journal of European Psychology Students}} % Committee
    {\href{https://blog.efpsa.org/2015/09/22/editors-pick-our-favourite-psychology-and-neuroscience-podcasts}{\textbf{Editor/Contributor [Link]}}} % Position
    {Jan. 2014 - May 2016} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Managed peer review process for 30 papers including paper submission, reviewer recruitment, copy editing, and publication.}
        \item {Contributor to popular psychology and neuroscience blog post, aimed at engaging aspiring psychology students.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
    
\cvsubsection{Education \& STEM Outreach}

%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {San Quentin State Prison} % Location
    {Prison University Project}
    {\href{https://www.neh.gov/about/awards/national-humanities-medals/prison-university-project}{\textbf{Lecturer [Link]}}} % Organization 
    {Jan. - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and lectured a new curriculum in General Psychology for incarcerated students. I brought human brains into the classroom to teach neuroanatomy, mirroring the UC Berkeley student experience. Provided executive board with formal analysis of organizational operations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  	{University of California, Berkeley} % Location
  	{Bay Area Scientists in Schools (BASIS)}
    {\href{https://docs.google.com/document/d/1EgLHC_wA5ZApCDpqfWc4APGsVKdoymPw/edit?usp=sharing&ouid=110847987931723045299&rtpof=true&sd=true}{\textbf{Team Member [Link]}}} % Organization 
    {Jan. 2018 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deployed neuroscience curriculum, "Know Your Brain", that has been presented to students in >20 Bay Area public schools.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Western University} % Location
    {Inspiring Young Women in STEM Inaugural Conference}
    {\href{https://www.inspiringdiversityinstem.com/2016-conference}{\textbf{Organizing Member [Link]}}} % Organization 
    {May 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Organizing member of first conference to encourage female students in STEM (>150 attendees), recruited keynote speakers, and evaluated research.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Western University}
    {Western Women Neuroscientists in Schools}
  	{\href{https://docs.google.com/presentation/d/1Dp3vELEXbNYQtvaOYiP4Rntj-JdygQvZ/edit?usp=sharing&ouid=110847987931723045299&rtpof=true&sd=true}{\textbf{Team Leader [Link]}}} % Organization
    {Oct. 2015 - May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and lectured curriculum to explore neuroscience misinformation ("Myths and the Brain"). Presented to >2000 high-schoolers in Ontario schools.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Western University}
    {Brain Bee}
  	{Volunteer} % Organization
    {May 2016 and May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of the organizing committee for the London Brain Bee, a neuroscience event that introduces high school students to neuroanatomy.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Trinity College, Dublin}
    {Student-to-Student (S2S)} % Committee
    {\textbf{Peer Mentor}} % Position
    {2011 - 2012} % Date(s)
    {
     \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided after-school homework support to children on the autism spectrum.}
      \end{cvitems}
   }
    
%---------------------------------------------------------
\end{cventries}
