%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Mentorship}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
 
%---------------------------------------------------------

  \cventry
    {\textbf{Cognitive Science; Psychology; Computer Science}} % Position
    {Undergraduate Students} % Student
    {\textbf{Supervisor}} % Position
    {15 hrs/week; Sep. 2019 - May 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item{Supervised and mentored four undergraduate students at the University of California, Berkeley in conducting scientific research for their honors thesis work. Managed the full cycle of their projects from initial concepts and experimental design to data analysis and final {\href{https://drive.google.com/file/d/1uhIOkii0y0wMr63KSzlhi7k7NqLEuFlU/view?usp=sharing}{poster \textit{[link]}}} and {\href{https://docs.google.com/presentation/d/1GmuGhTJFQFXBuVG_8zfoTIu2ForG47HIdeSV-09GFe8/edit?usp=sharing}{conference \textit{[link]}}} presentation. All students were supervised during the COVID-19 pandemic, which required the development of efficient communication strategies, as well as flexibility and adaptability in coordinating project time-lines.}.
      \end{cvitems}
    }
    
    
%---------------------------------------------------------
  %\cventry
  	%{\textbf{Psychology; Computer Science}}
   % {Undergraduate Research Assistants} % Student
   % {Supervisor}
   	%{Jan. - May 2021; Sep. 2019 - May 2020} % Date(s)
   % {
      %\begin{cvitems} % Description(s) of tasks/responsibilities
      %  \item{Supervised 
      %  \item {Zanib Naaem tested \textit{30} college-aged students on a multi-session eye-tracking and behavioral learning project (during COVID-19 pandemic).}
      %  \item {Yiling Kao tested \textit{50} participants and used machine learning to study speech envelopes, now works at Microsoft as software engineer.}
      %\end{cvitems}
    %}
    
%---------------------------------------------------------
  \cventry
  	{\textbf{Neuroscience}}
    {Ph.D. Students} % Student
    {\textbf{Supervisor}}
    {5 hrs/week; Sep. 2018 - Dec. 2020} % Date(s)
   {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and managed collaborative projects with 3 first-year Ph.D. students, two of whom were supervised during the COVID-19 pandemic. Projects included a meta-analysis of brain connectivity, computational models of neural data {\href{https://docs.google.com/presentation/d/1KqypbxIWP9h1bFufipUan3MAQW_0ZS7i/edit?usp=sharing&ouid=110847987931723045299&rtpof=true&sd=true}{\textit{[link]}}}, and cross-integration of clinical platforms. Advocated on behalf of the students to present their research findings at departmental seminars}. 
      \end{cvitems}
    }
    
%---------------------------------------------------------
 % \cventry
 %   {Sep. - Dec. 2018} % Date(s)
 %   {Post-Baccalaureate Students} % Student
 %%   {\textbf{Dylan Benkley}}
 %   {Psychology}
 %  {
    %  \begin{cvitems} % Description(s) of tasks/responsibilities
    %    \item {Dylan Benkley conducted a literature review on the role of the cerebellum in social cognition.}
    %  \end{cvitems}
    %}

%---------------------------------------------------------
\end{cventries}
