%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Public Service \& Outreach}

%-------------------------------------------------------------------------------
\cvsubsection{Committees \& Policy}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry 
    {University of California, Berkeley} % Location
    {Graduate Assembly Students of Psychology}
    {\textbf{Member and RSO Signatory}} % Organization
    {Sep. 2018 - Mar. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided data analytics to improve efficiency of phone banking for Psychology "Big Give". Contacted 10-fold more donors than previous year.}
        \item {Liaison officer between Berkeley development office and external donors. Organized faculty fundraisers in Silicon Valley, fund-raising \$15,000.}
      \end{cvitems}
    }
    
  \cventry
    {European Union}
    {European Federation of Psychology Students' Association} % Committee
    {\href{https://jeps.efpsa.org/articles/10.5334/jeps.401/}{\textbf{Editor [Link]}}} % Position
    {Jan. 2016 - May 2016} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheaded initiative to pre-register scientific results in the Journal of European Psychology Students, a first for student journals worldwide.}
        \item {Advised organization leadership on best practices for successful implementation of pre-registration and authored journal article (>3500 views).}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
  	{Western University} % Location
  	{Schulich School of Medicine Graduate Council} % Committee
    {\textbf{Secretary}} % Position
    {Sep. 2015 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided budget evaluation of graduate student insurance plan to council. Served as student liaison officer, and oversaw a budget of \$5000}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
  	{Trinity College, Dublin}
  	{Niteline (Student Helpline)} % Committee
    {\textbf{Publicity Officer}} % Position
    {Sep. 2011 - May 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided practical program consultation to student helpline \href{https://niteline.ie/}{\textit{[link]}}, and wrote proposal to increase the yearly budget from \$5,000 to \$10,000.}
      \end{cvitems}
    }

\cvsubsection{Communication \& Administration}

%---------------------------------------------------------
  \cventry 
    {University of California, Berkeley} % Location
    {Graduate Assembly Students of Psychology}
    {\href{https://psychblog.berkeley.edu/opinion/2019/09/09/Graduate-School-Advice/}{\textbf{Writer/Contributor [Link]}}} % Organization
    {Sep. 2019 - May 2021} % Date(s)
    {
      \begin{cvitems} 
      	\item {Created, managed, and edited Berkeley Psychology blog to spotlight graduate student research. Increased monthly viewers 5-fold.}
      	\item {Co-founded and operated Twitter account for Berkeley Psychology \href{https://twitter.com/BerkeleyPsych}{\textit{[link]}}. Increased follower count to >1500 after 2 years.}
      	\item {Lead writer of Psychology newsletter \href{https://psychology.berkeley.edu/sites/default/files/newsletters/2021spr_fullnewsletter_v2.pdf}{\textit{[link]}} (>2000 circulation). Included profiles on graduates to strengthen ties with alumni community.}
      \end{cvitems}
    }
    
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {European Union}
    {\textbf{Journal of European Psychology Students}} % Committee
    {\href{https://blog.efpsa.org/2015/09/22/editors-pick-our-favourite-psychology-and-neuroscience-podcasts}{\textbf{Editor/Contributor [Link]}}} % Position
    {Jan. 2014 - May 2016} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Managed peer review process for 30 papers including paper submission, reviewer recruitment, copy editing, and publication.}
        \item {Contributor to popular psychology and neuroscience blog post, aimed at engaging aspiring psychology students (>500 monthly views).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
    
\cvsubsection{Education \& STEM Outreach}

%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {San Quentin State Prison} % Location
    {Prison University Project}
    {\href{https://www.neh.gov/about/awards/national-humanities-medals/prison-university-project}{\textbf{Lecturer [Link]}}} % Organization 
    {Jan. - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and lectured a new curriculum in General Psychology for incarcerated students. I brought human brains into the classroom to teach neuroanatomy, mirroring the UC Berkeley student experience. Provided executive board with formal analysis of organizational operations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  	{University of California, Berkeley} % Location
  	{Bay Area Scientists in Schools (BASIS)}
    {\href{https://docs.google.com/document/d/1EgLHC_wA5ZApCDpqfWc4APGsVKdoymPw/edit?usp=sharing&ouid=110847987931723045299&rtpof=true&sd=true}{\textbf{Team Member [Link]}}} % Organization 
    {Jan. 2018 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-developed and deployed neuroscience curriculum, "Know Your Brain", that has been presented to students in >20 Bay Area public schools.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Western University} % Location
    {Inspiring Young Women in STEM Inaugural Conference}
    {\href{https://www.inspiringdiversityinstem.com/2016-conference}{\textbf{Organizing Member [Link]}}} % Organization 
    {May 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-organized first conference to encourage female students in STEM (>150 attendees), recruited keynote speakers, and evaluated research.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Western University}
    {Western Women Neuroscientists in Schools}
  	{\href{https://docs.google.com/presentation/d/1Dp3vELEXbNYQtvaOYiP4Rntj-JdygQvZ/edit?usp=sharing&ouid=110847987931723045299&rtpof=true&sd=true}{\textbf{Team Leader [Link]}}} % Organization
    {Oct. 2015 - May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed curriculum to explore neuroscience misinformation ("Myths and the Brain"). Presented to >2000 high-schoolers in Ontario schools.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
 % \cventry
    %{Western University}
    %{Brain Bee}
  	%{Volunteer} % Organization
    %{May 2016 and May 2017} % Date(s)
    %{
     % \begin{cvitems} % Description(s) of tasks/responsibilities
       % \item {Member of the \textbf{organizing committee} for the London Brain Bee, a neuroscience event that introduces \textbf{high school students} to neuroanatomy.}
     % \end{cvitems}
    %}
    
%---------------------------------------------------------
%  \cventry
 %   {Trinity College, Dublin}
 %   {Student-to-Student (S2S)} % Committee
 %   {\textbf{Peer Mentor}} % Position
 %   {2011 - 2012} % Date(s)
 %   {
 %    \begin{cvitems} % Description(s) of tasks/responsibilities
 %       \item {Provided after-school \textit{homework support} to \textit{children} on the autism spectrum.}
 %     \end{cvitems}
 %   }
    
%---------------------------------------------------------
\end{cventries}
