
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected Projects}

%-------------------------------------------------------------------------------
\cvsubsection{Policy \& Management}

%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry 
    {Department of Psychology, University of California, Berkeley} % Location
    {Graduate Mentoring Policies}
    {\href{http://ivrylab.berkeley.edu/uploads/4/1/1/5/41152143/cognac_lab_policies_19feb2021.pdf}{\textbf{Co-Chair [Link]}}} % Organization
    {Jan. 2020 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Recognized need for formal mentor-mentee agreements in the UC Berkeley psychology department. Assembled and co-led working committee to create policy to improve lab culture and mentor-mentee relationships. Recruited panelists from diverse backgrounds.}
        \item {Authored 10-page policy document on mentorship and lab policy agreements. Advised leadership on implementation of new departmental policies during quarterly climate and equity meetings. Since Sep. 2021, 35/42 faculty have created lab policy documents.}
      \end{cvitems}
    }
    
    
%---------------------------------------------------------
  \cventry 
    {Department of Psychology, University of California, Berkeley} % Location
    {State of the Department Initiative}
    {\href{https://drive.google.com/file/d/1wD7y5gW39EU4vQUyhcrO7Fra1Ttc_HyG/view?usp=sharing}{\textbf{Leader [Link]}}} % Organization
    {Apr. 2019 - Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Team leader for faculty accountability initiative. Developed survey for Berkeley Psychology state of the department annual meeting, and conducted data analytics and statistics to translate graduate student concerns into policy recommendations. Used data and statistics to highlight funding discrepancy between neuroscience and clinical psychology students, resulting in a 20\% yearly increase in graduate student stipends.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

%-------------------------------------------------------------------------------
\cvsubsection{Data Science \& Information Technology}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    
%---------------------------------------------------------
  \cventry
    {University of California, Berkeley; Western University} % Date(s)
  	{SUITPy: Open-source package for the visualization of cerebellum imaging data} % Organization
  	{\href{https://suitpy.readthedocs.io/en/latest/}{\textbf{Developer [Link]}}}
  	{Jan. - Sep. 2021}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Core developer of SUITPy, an open-source Python library to visualize brain data. Subsequently worked as project manager to identify best programming practices for improving core functionality, resulting in record monthly installations (4-fold increase).}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  %\cventry
  %  {Jan. - Sep. 2021} % Date(s)
  %  {Evaluating functional boundaries of the brain using a novel distance coefficient} % Organization
  %  {\href{https://www.biorxiv.org/content/10.1101/2021.05.11.443151v1.full.pdf}{\textbf{Paper [Link]}}}
  %  {}
  %  {
   %   \begin{cvitems} % Description(s) of tasks/responsibilities
   %     \item {Co-developed a novel \textit{statistical metric} to evaluate the validity of \textit{brain parcellations}, an advancement on \textit{Homogeneity and Silhouette coefficients}. Evaluated metric on \textit{open-source} brain data from \href{http://www.humanconnectomeproject.org/}{\textit{Human Connectome Project}}.}
     % \end{cvitems}
   % }
    
 %---------------------------------------------------------
 %\cventry
   % {2021} % Date(s)
   % {Predicting brain activation maps for arbitrary tasks with cognitive encoding models} % Organization
   % {\href{https://drive.google.com/file/d/1dRNSsRzGSSF9QJLJv_jK1R7BmmWfOsMt/view}{\textbf{Poster [Link]}}}
   % {}
    %{
     % \begin{cvitems} % Description(s) of tasks/responsibilities
      	%\item {Evaluated cognitive \textit{encoding models} on brain data and used \textit{natural language processing} to extract features from a formal \textit{cognitive ontology}.}
     % \end{cvitems}
   % }     

%---------------------------------------------------------
  \cventry
   	{Department of Psychology, University of California, Berkeley}
    {Predicting human performance using computer vision models} % Organization
    {\href{https://github.com/maedbhk/action_prediction}{\textbf{Github [link]}}}
    {Jan. 2019 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Recorded >15 hours of varsity athletes, and implemented markerless labeling of videos to understand human performance in predicting action.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Helen Wills Neuroscience Institute, University of California, Berkeley} % Date(s)
    {Low dimensional embedding of genetic gradients in the human cerebellum} % Organization
    {\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3797269}{\textbf{Author [Link]}}}
    {May 2019 - Sep. 2021}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Initiated collaboration with incoming faculty at Berkeley to investigate genetic gradients in the human cerebellum. Learned new statistical tools to analyze postmortem human brain data, and developed pipelines to streamline data preprocessing, later adopted by >5 students.}
      \end{cvitems}
    }
  
\end{cventries}
    
\cvsubsection{Public Health}

\begin{cventries}

%---------------------------------------------------------
 \cventry
   {School of Information, University of California, Berkeley} % Date(s)
   {Predicting COVID-19 mortality rates across the U.S. using mobility and census data} % Organization
    {\href{https://drive.google.com/file/d/1l9TLGLmstkJsvOJQPxHe_f35b4fEkDU4/view}{\textbf{Author [Link]}}}
    {Sep. - Dec. 2020}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Built a statistical model predicting COVID-19 deaths in the U.S. from May - Aug. 2020 using data from the U.S. Census and Google Maps mobility reports. Increased optimization of algorithm by 20-fold. Presented findings in a poster presentation to faculty in the School of Information.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry 
    {University of California, Berkeley; Princeton University; Yale University} % Date(s)
    {Cross-Functional and Cross-Disciplinary Research Collaboration}
    {\href{http://www.actcompthink.org/pubs/McDougleTsayEtAl_2021.pdf}{\textbf{Team Leader}}} % Organization
    {Jan. 2019 - May. 2020} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Implemented and maintained data warehousing for clinical research projects, established guidelines for cross-functional collaboration.}
      \end{cvitems}
    } 

%---------------------------------------------------------
  \cventry 
    {Cognition and Action Lab, University of California, Berkeley} % Location
    {Ethics Protocol for MRI projects}
    {\href{https://drive.google.com/file/d/1h66emU7-TRl-mSLZTEH01E3Qf5ZpEdbv/view?usp=sharing}{\textbf{Manager [Link]}}} % Organization
    {Jan. 2018 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Drafted guidelines and maintained ethics protocol for institutional review board (IRB) magnetic resonance imaging (MRI) projects. Completed human research program on "Human Research: Biomedical Research Investigators", and trained 3 research assistants on the protocol.}
      \end{cvitems}
    }
 
%---------------------------------------------------------
\end{cventries}