%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Teaching}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {Mount Tamalpais College} % University
    {General Psychology} % Course
    {\href{https://docs.google.com/document/d/1CCjwp7zmqr76HUuSvEF3AMZFzeTBhddgNd5zSgZBDeA/edit?usp=sharing}{\textbf{Lecturer [Link]}}} % Role
    {Sep. - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and lectured course on general psychology to incarcerated students. Topics included "the brain and nervous system", "classical conditioning", and "mood disorders". Devised trauma-informed learning objectives, catering to students with diverse educational needs.}  
      \end{cvitems}
    }
    
 %---------------------------------------------------------
  \cventry
	{University of California, Berkeley} % Role
	{Biological Psychology, PSYCH 110; Cognitive Neuroscience, PSYCH 127} % Course
    {\href{https://docs.google.com/document/d/1rZl_JGgukSODwxE-vGzaTSg-20NvZqk4/edit?usp=sharing&ouid=110847987931723045299&rtpof=true&sd=true}{\textbf{Instructor [Link]}}} % University
    {Aug. - Dec. 2018; Aug. - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Instructed weekly seminars for 120+ students on topics including "memory and learning" and "ethics of artificial intelligence", under the supervision of UC Berkeley professors. Evaluated and supervised student research and wrote professional references for promising students.}
      \end{cvitems}
    }
    
 %---------------------------------------------------------
  \cventry
	{Western University} % Role
	{Biology/Statistics, STAT 2244; Probability and Statistics, STAT 2857} % Course
    {\href{https://drive.google.com/file/d/1vOkiycHtsmuYfOwiYWny_tI0iOJ-Km9m/view?usp=sharing}{\textbf{Instructor [Link]}}} % University
    {Jan. 2016 - May. 2017; Jan. - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Instructed undergraduate students in a statistics and data science laboratory using the programming language "R". Topics included "central limits theorem", "hypothesis testing" and "conditional probability". Wrote and administered exams and evaluated student work.}
      \end{cvitems}
    }
    
    
%---------------------------------------------------------
\end{cventries}
