%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Leadership \& Service}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    
%---------------------------------------------------------
  \cventry 
    {University of California, Berkeley} % Location
    {Graduate Assembly Students of Psychology}
    {\textbf{Member and RSO Signatory}} % Organization
    {Sep. 2018 - } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textit{Created}, \textit{mangaged}, and \textit{edited} Berkeley Psychology blog to \textit{spotlight} graduate student research.}
        \item {\textit{Co-founded and operated} Twitter account for Berkeley Psychology.}
        \item {\textit{Writer and contributor} of Berkeley Psychology \textit{newsletter}.}
        \item {\textit{Data analysis, statistics, visualization} for Berkeley Psychology \textit{state of the department} annual meeting.}
        \item {Co-organized \textit{faculty fundraisers} in Silicon Valley and co-led Psychology \textit{"Big Give"} to fund-raise for Berkeley Psychology.}
        \item {Assembled \textit{working committee} to improve \textit{lab culture} and mentor-mentee relationships, co-wrote \textit{mentorship and lab policy agreements} resulting in new departmental \textit{policies} on mentorship.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Richmond, California} % Location
    {Prison University Project}
    {\textbf{Volunteer and Lecturer}} % Organization 
    {Sep. 2019 - Mar. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textit{Designed} and \textit{lectured} a course in General Psychology to incarcerated students in \textit{San Quentin State Prison}.}
        \item {Created care packages and holiday art for incarcerated people in California prisons during the \textit{COVID-19 pandemic}.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
  	{University of California, Berkeley} % Location
  	{Bay Area Scientists in Schools (BASIS)}
    {\textbf{Volunteer}} % Organization 
    {Jan. 2018 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textit{Presented} multiple lectures on the "Feel Human Brains" to \textit{elementary school children} in Bay Area schools.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
