%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Ph.D. in Cognitive Neuroscience (GPA: 3.96/4.00)} % Degree
    {University of California, Berkeley} % Institution
    {\textbf{Berkeley, California}} % Location
    {Sep. 2017 - Expected: May. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {{\href{http://ivrylab.berkeley.edu/rich-ivry.html}{\textbf{Advisor: Richard Ivry, Ph.D.}}}}
        \item {{\href{https://www.ischool.berkeley.edu/programs/data-science-certificate}{Applied Data Science Certificate, School of Information.}}\textit{Awards: Mark R. Rosenzweig Graduate Fellowship (2021); Cognitive Computational Neuroscience Travel Award (2020)}}
        %\item {\textit{Awards: Mark R. Rosenzweig Graduate Fellowship (2021); Cognitive Computational Neuroscience Travel Award (2020)}}
      \end{cvitems}
    }

%---------------------------------------------------------	
  \cventry
    {M.Sc. in Neuroscience (GPA: 4.0)} % Degree
    {Western University} % Institution
    {\textbf{London, Ontario}} % Location
    {Sep. 2015 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {{\href{http://www.diedrichsenlab.org/}{\textbf{Advisor: Joern Diedrichsen, Ph.D.}}} \textit{Awards: Gordon Cerebellum Student Travel Award (2017)}}
       % \item {\textit{Awards: Gordon Cerebellum Student Travel Award (2017)}}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {B.A. in Psychology and French (Double Major; GPA: 4.0)} % Degree
    {Trinity College Dublin} % Institution
    {\textbf{Dublin, Ireland}} % Location
    {Sep. 2010 - May. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {{\href{https://oconnell-lab.com/home/meet-the-team/redmond-oconnell/}{\textbf{Advisor: Redmond O'Connell, Ph.D.}}} \textit{Awards: Irish Research Council Postgraduate Scholarship (2015); Ussher Fellowship, Trinity College Dublin (2015); US Fulbright Program (shortlisted); Wellcome Trust Biomedical Scholarship (2014); Entrance Scholarship, Trinity College Dublin}}
       % \item {\textit{Awards: Irish Research Council Postgraduate Scholarship (2015); Ussher Fellowship, Trinity College Dublin (2015); US Fulbright Program (shortlisted); Wellcome Trust Biomedical Scholarship (2014); Entrance Scholarship, Trinity College Dublin}}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
