%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Mentorship}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
 
%---------------------------------------------------------

  \cventry
    {Sep. 2019 - May 2021} % Date(s)
    {Honors Thesis Students {\href{https://drive.google.com/file/d/1uhIOkii0y0wMr63KSzlhi7k7NqLEuFlU/view?usp=sharing}{\textbf{[Link]}}\href{https://docs.google.com/presentation/d/1GmuGhTJFQFXBuVG_8zfoTIu2ForG47HIdeSV-09GFe8/edit?usp=sharing}{\textbf{[Link]}}}} % Student
    {Cognitive Science; Psychology} % Position
    {\textbf{Shannon Lee; Sienna Bruinsma}} 
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Shannon Lee tested \textit{50} participants (during COVID-19 pandemic) and wrote her thesis on eye-tracking models that inform social learning.}
        \item {Sienna Bruinsma tested \textit{25} patients with ataxia (during COVID-19 pandemic) and wrote her thesis on cerebellar function in language.}
      \end{cvitems}
    }
    
    
%---------------------------------------------------------
  \cventry
    {Jan. - May 2021; Sep. 2019 - May 2020} % Date(s)
    {Undergraduate Research Assistants} % Student
    {Psychology; Computer Science}
   	{\textbf{Zanib Naaem; Yiling Kao}}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Zanib Naaem tested \textit{30} college-aged students on a multi-session eye-tracking and behavioral learning project.}
        \item {Yiling Kao tested \textit{50} participants and used machine learning to study speech envelopes.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Sep. - Dec. 2020; Jan. - May 2020; Sep. - Dec. 2018} % Date(s)
    {Ph.D. Rotation Students} % Student
    {Neuroscience}
    {\textbf{Amanda LeBel; Jacob Ziontz; Mark Gorenstein}}
   {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Amanda LeBel developed encoding models using speech features to study task-evoked cerebellar activity.}
        \item {Jacob Ziontz set up fMRI preprocessing scripts on multi-session cerebellar data using high performance computing.}
        \item {Mark Gorenstein did a meta-analysis of quantitative models for understanding brain connectivity.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
 % \cventry
 %   {Sep. - Dec. 2018} % Date(s)
 %   {Post-Baccalaureate Students} % Student
 %%   {\textbf{Dylan Benkley}}
 %   {Psychology}
 %  {
    %  \begin{cvitems} % Description(s) of tasks/responsibilities
    %    \item {Dylan Benkley conducted a literature review on the role of the cerebellum in social cognition.}
    %  \end{cvitems}
    %}

%---------------------------------------------------------
\end{cventries}
