%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Teaching}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {Lecturer} % Role
    {\href{https://docs.google.com/document/d/1CCjwp7zmqr76HUuSvEF3AMZFzeTBhddgNd5zSgZBDeA/edit?usp=sharing}{\textbf{General Psychology [Link]}}} % Course
    {\textbf{Mount Tamalpais College}} % University
    {Sep. - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and lectured course on general psychology to incarcerated students. Topics included "the brain and nervous system", "classical conditioning", and "mood disorders". Devised trauma-informed learning objectives, catering to students with diverse educational needs.}  
      \end{cvitems}
    }
    
 %---------------------------------------------------------
  \cventry
	{Graduate Student Instructor} % Role
	{Biological Psychology, PSYCH 110; Cognitive Neuroscience, PSYCH 127} % Course
    {\textbf{University of California, Berkeley}} % University
    {Aug. - Dec. 2018 and Aug. - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Instructed weekly seminars for 120+ students on topics including "memory and learning" and "ethics of artificial intelligence", under the supervision of UC Berkeley professors. Evaluated and supervised student research and wrote professional references for promising students.}
      \end{cvitems}
    }
    
 %---------------------------------------------------------
  \cventry
	{Graduate Student Instructor} % Role
	{Introduction to Statistics, STAT 1024; Probability and Statistics, STAT 2857} % Course
    {\textbf{Western University}} % University
    {Jan. - May. 2017; Sep. - Dec. 2016 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Instructed undergraduate students in a statistics and data science laboratory using the programming language "R". Topics included "central limits theorem", "hypothesis testing" and "conditional probability". Wrote and administered exams and evaluated student work.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}
