%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Outreach}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Member and RSO Signatory} % Organization
    {Graduate Assembly Students of Psychology} 
    {University of California, Berkeley} % Location
    {Sep. 2018 - } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created Berkeley Psychology blog intended to spotlight graduate student research.}
        \item {Co-founded and operated twitter account for Berkeley Psychology.}
        \item {Writer/Contributor of Berkeley Psychology newsletter.}
        \item {Data analysis, statistics and visualization for Psychology state of the department annual meeting.}
        \item {Co-wrote mentorship agreement and lab policy documents for Berkeley psychology.}
        \item {Member of fundraising committee, attended Berkeley Psychology faculty talks in Silicon Valley.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Volunteer} % Organization
    {Prison University Project} 
    {Richmond, California} % Location
    %{Berkeley, California}
    {Sep. 2020-} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {During the COVID-19 pandemic, created care packages and holiday art for incarcerated people in California prisons.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Volunteer} % Organization
    {Bay Area Scientists in Schools (BASIS)} 
    {University of California, Berkeley} % Location
    %{Berkeley, California}
    {Jan. 2018 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Presented multiple lectures on the "Feel Human Brains" to elementary school children in Bay Area schools.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Organizing Member} % Organization
    {Inspiring Young Women in STEM Inaugural Conference} 
    {Western University} % Location
    %{London, Ontario}
    {2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Recruited keynote speakers and evaluated student research.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
  	{Volunteer} % Organization
    {Western Women Neuroscientists in Schools}
    {Western University}
    %{London, Ontario} % Location
    {Oct. 2015 - May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Presented multiple lectures on "Myths and the Brain" to secondary school children in London, Ontario schools.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
  	{Volunteer} % Organization
    {Brain Bee}
    {Western University}
    %{London, Ontario} % Location
    {May 2016 and May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of the organizing committee for the London Brain Bee, a neuroscience event that introduces high school students to neuroanatomy.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Secretary} % Position
    {Schulich School of Medicine Graduate Council} % Committee
    {Western University} % Location
    %{London, Ontario} % Location
    {2015 - 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Took notes at biweekly committee meetings and voted on council plans.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Junior Editor} % Position
    {Journal of European Psychology Students} % Committee
    {European Federation of Psychology Students' Association}
    {2014 - 2016} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Edited research/review paper submissions, recruited reviewers, copy editors, and communicated decision outcome to authors.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Publicity Officer and Volunteer} % Position
    {Niteline (Student Helpline)} % Committee
    {Trinity College, Dublin}
    %{Dublin, Ireland}
    {2011 - 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided crisis support to students and publicized the student helpline services at national events.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Peer Mentor} % Position
    {Student-to-Student (S2S)} % Committee
    {Trinity College, Dublin}
    %{Dublin, Ireland}
    {2011 - 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided after-school homework support to children on the autism spectrum.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
