%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry 
    {2022-present} % Location
    {Massachusetts Institute of Technology}
    {Postdoctoral Associate} % Organization
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Directed a cross-functional project on suicide prediction, bridging clinicians, software engineers, and scientists from MIT and the University of Pennsylvania. Designed large language modeling pipelines using electronic health records to identify racial bias in machine learning models.}
        \item {Managed a team of undergraduates to develop interpretable artificial intelligence pipelines. We then applied these pipelines to large-scale datasets, investigating the relationship between individual and sex-based variation and symptoms of neurodevelopmental disorders such as ADHD.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry 
    {2024-present} % Location
    {Harvard Medical School}
    {Teaching Fellow} % Organization
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Facilitated learning as a Teaching Fellow for a psychopathology course at Harvard Medical School, delivering review sessions, managing student engagement, and providing organizational and technical support, while acting as a key liaison between students and course directors.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry 
    {2023-present} % Location
    {MIT Science Policy Review}
    {Co-Editor and Lead Author} % Organization
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Interviews co-editor for Vol. VI, curated and managed interviews with high-profile changemakers, notably Nobel Prize economists and leading journalists from the Boston Globe, and directed the entire editorial workflow, from conception to publication.}
        \item {Strategically led a collaborative effort for Vol. V to inform policy on precision medicine for neuropsychiatry, resulting in a first-authored policy paper designed to inform academics and policymakers on the pitfalls and promises of personalized medicine for psychiatry.}
      \end{cvitems}
    }
    
      %---------------------------------------------------------
  \cventry
    {2017-2022}
    {University of California, Berkeley} % Job title
    {Graduate Student Researcher}
    {} % Organization
    {
      \begin{cvitems} 
        \item {15 publications (>1000 citations), including first authorship in \#1 neuroscience journal \textit{Nature Neuroscience} for my work using advanced neuroimaging and clinical neuropsychology to map and model the adult human cerebellum. Named in the top 0.5\% of all scholars worldwide by \textit{ScholarGPS} for \textit{"strong publication record and impact of your work"}, and publicized in popular media including Knowable Magazine and Psychology Today.}  
        \item {Delivered instruction for undergraduate courses including Biological Psychology and Cognitive Neuroscience at UC Berkeley. I also developed and delivered a course in General Psychology to incarcerated students at San Quentin State Prison adopting a trauma-informed curriculum.}
		\end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}



