%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Leadership}

%\cvsubsection{Policy}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry 
    {MIT Council on Family and Work ('23-'24)} % Location
    {}
    {}
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As a nominated member, I analyzed parental leave/childcare policies via university-wide survey, informing recommendations to senior leadership.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry 
    {UC Berkeley Graduate Assembly ('20-'22)} % Location
    {}
    {} % Organization
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Co-led a departmental initiative to establish formal mentor-mentee agreements, resulting in a 10-page policy proposal, adopted by 90\% of faculty.}
      \item{Served as a liaison between the Berkeley development office and external donors. Led fundraising initiatives for faculty in Silicon Valley.}
      \item{Launched and managed the Berkeley Psychology blog to spotlight graduate student research. Published and edited >10 pieces during my tenure.}
      \item {Managed data-driven initiatives to optimize fundraising and advocacy efforts, resulting in a 20\% increase in graduate stipends for Psychology students.}
      \end{cvitems}
      }   
       
  \cventry  
    {European Federation of Psychology Students' Association}
    {} % Committee
    {} % Position
    {} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Pioneered the implementation of pre-registration for the Journal of European Psychology Students, setting a new global standard for student journals.}
      \end{cvitems}
      }

%---------------------------------------------------------
\end{cventries}



