%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Mapping networks of the human brain during learning, publications in \textit{Brain}, \textit{Neuron}, \textit{Nature Neuroscience}}
    {Ph.D. Graduate Researcher (2017-2022)} % Job title
    {\href{https://github.com/maedbhk/cerebellum_learning_connect}{\textbf{Github [link]}}}
    {University of California, Berkeley} % Action and Cognition Laboratory
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed machine learning pipelines to predict cognitive function in the human cerebellum during learning, tested patients with spinocerebellar ataxia on a series of cognitive tasks to assess impairments, analyzed post-mortem brains to create a transcriptomic map of the human cerebellum.}
        \item {Designed a longitudinal study to model human learning. Led and managed a team of 5 to collect 300 experimental hours of biological data including functional magnetic resonance imaging (fMRI), eye-tracking, and physiological data (during COVID-19 pandemic).}
        \item {Co-wrote an R35 grant that received 5-year funding from the NIH. Managed an institutional review board (IRB) protocol for fMRI experiments.}
        \item {Created a widely adopted mentorship agreement for research assistants to ensure transparency and accountability in mentoring practices. Co-led a journal club for undergraduate research assistants, instructing them on the scientific method, data analysis, and statistics.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Developing novel brain maps of the human cerebellum, publications in \textit{Brain}, \textit{NeuroImage}, \textit{Frontiers}}
    {M.Sc. Graduate Researcher (2015-2017)} % Job title
    {\href{http://ivrylab.berkeley.edu/uploads/4/1/1/5/41152143/functional_boundaries_in_the_human_cerebellum.pdf}{\textbf{Paper [link]}}}
    {Western University} % Motor Control Laboratory
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        %\item {My thesis used \textit{machine learning} to map cognitive sub-domains of the human cerebellum.}
      	\item {Created a novel map of the human cerebellum by applying matrix factorization to high-dimensional neural data {\href{http://www.diedrichsenlab.org/imaging/mdtb.htm}{[\textit{link}}]}.}
      	\item {Initiated a collaboration with scientists from Stanford University to use natural language processing and regularized regression to assign cognitive labels {\href{https://cognitiveatlas.org/}{\textit{[link]}}} to the human cerebellum. Invested in open-source science, the data are publicly available and have been downloaded >200 times {\href{https://openneuro.org/datasets/ds002105/versions/1.1.0}{[\textit{link}}]}.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}

%-------------------------------------------------------------------------------
\cvsubsection{Research Impact}

%-------------------------------------------------------------------------------
\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {The mysterious, multifaceted cerebellum} % Title
    {Knowable Magazine}
    {\href{https://knowablemagazine.org/article/mind/2020/what-does-the-cerebellum-do}{\textbf{link}}}
    {2020}

%---------------------------------------------------------
  \cvhonor
    {Scientists map our underappreciated "little brain"} % Title
    {University of California, Berkeley}
    {\href{https://news.berkeley.edu/story_jump/cerebellum-map/}{\textbf{link}}}
    {2019}
    
%---------------------------------------------------------
  \cvhonor
    {New maps of the cerebellum show how our "little brain" works} % Title
    {Psychology Today}
    {\href{https://www.psychologytoday.com/us/blog/the-athletes-way/201907/new-maps-the-cerebellum-show-how-our-little-brain-works}{\textbf{link}}}
    {2019}
    
  %\cvhonor
   % {Educational Symposium: Neuroanatomy for neuroimaging} % Event
   % {Organization for Human Brain Mapping} % Title
   % { \href{https://www.youtube.com/watch?v=L6nwkvBqJzI}{\textbf{link}}} % Location
   % {2021} % Date(s)

%---------------------------------------------------------
\end{cvhonors}
